---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This is a collection of functions to make working with data from the [HCAI DCS](https://hcaidcs.phe.org.uk/) easier. 
The plan is to include Rmd documents to produce the IS six-monthly reports and other standard outputs, including the quarterly epidemiologic commentary. 

## Installation

The quickest way to install the package is to use `install_git` from the devtools package. 

```{r, eval=FALSE}
# install devtools if necessary
install.packages("devtools")

# then install the hcaidcs package
devtools::install_git('https://gitlab.phe.gov.uk/Simon.Thelwall/hcaidcs.git')
```

Alternatively, one can download the zip file from gitlab and do the following:

1.	Save the zip file to `H:\`     but do not unzip
1.	Open RStudio
1.	Run the following line: `install.packages(file.choose(), repos=NULL)`
1.	This will launch a file chooser where you can select the zip file you have just downloaded. 

This should install the package to the R package library. 

If installation is successful you will then be able to load the package with
`library(hcaidcs)`

## Use
Functions that begin `aec_` are intended for producing tables or plots for the annual epidemiologic commentary. 

Functions beginning `ann_tab_` are intended for the production of the annual tables. 

Functions prefixed `nice_` indicate that they format values for nice printing in text, such as financial year, or an estimate with its' 95% confidence interval. 

Functions prefixed `kh03_` indicate functions for use in the preparation of the kh03 denominator data. 

Functions prefixed `mf_` indicate functions for use in the preparation of the HCAI monthly factsheet for the department of health. 

## Contributions
Contributions to this package are welcome. 
Please see the [Contribution guidelines](http://bioinformatics-git.phe.gov.uk/Simon.Thelwall/hcaidcs/blob/master/CONTRIBUTING.md).
